Tropical Andes plant occurrence data GBIF

### 2023-08-01 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
adding code to subset to Tropical Andes lowland and montane forest

# Load required packages
```{r}
library(dplyr)
library(rgbif) 
```

@@

>>>>

# Load required packages
```{r}
library(dplyr)
library(rgbif)
library(raster)
library(sf)
```

@@

# Subset to Tropical Andes Lowland and Montane Forest
```{r}
TropicalAndes_IUCNHabitat_Forest <- st_read(file.path(data_path, "TropicalAndes_IUCNHabitat_Forest.shp"))
# convert dataframe to spatial object
coordinates(d) <- ~decimalLatitude+decimalLongitude
crs(d) <- crs(TropicalAndes_IUCNHabitat_Forest)
```

```{r}
GBIF_Forest <- d %>% filter(TropicalAndes_IUCNHabitat_Forest)
GBIF_Forest
plot(GBIF_Forest)
```
